Physcraper: Body

### 2020-07-22 2-body.Rmd
all comments added

```{r framework, echo=FALSE, fig.cap="The Physcraper software is fully described on its documentation website at https://physcraper.readthedocs.io/en/latest/, along with installation instructions, tutorials, examples and function usage documentation.", out.width = '85%', fig.retina= 2, fig.align = "center"}
knitr::include_graphics("https://raw.githubusercontent.com/McTavishLab/physcraper/pyopensci/docs/img/schematic.svg")
# knitr::include_graphics("docs/figs/schematic.svg")
```

>>>>

```{r framework, echo=FALSE, fig.cap="The Physcraper software is fully described on its documentation website at https://physcraper.readthedocs.io/en/latest/, along with installation instructions, tutorials, examples and function usage documentation.", out.width = '85%', fig.retina= 2, fig.align = "center"}
# knitr::include_graphics("https://raw.githubusercontent.com/McTavishLab/physcraper/pyopensci/docs/img/schematic.svg")
knitr::include_graphics("docs/figs/schematic.svg")
```
